---
title: "Notepad"
output: html_document
---

```{r, message=FALSE}
#libraries:

library(tidyverse)
library(gridExtra)
library(grid)
library(randomForest)
library(caret)
library(rpart)
library(Polychrome)
library(pROC)
library(klaR)
library(FactoMineR)
library(factoextra)
library(Rtsne)
library(cluster)

# dataloading:

ade <- read.csv('source_data/ad_events.csv')
ads <- read.csv('derived_data/ads_cleaned.csv') %>% dplyr::select(-X)
camp <- read.csv('source_data/campaigns.csv')
users <- read.csv('derived_data/user_cleaned.csv') %>% dplyr::select(-X)
comp1 <- read.csv('derived_data/composite_data1.csv') %>% dplyr::select(-X)
comp2 <- read.csv('derived_data/composite_data2.csv') %>% dplyr::select(-X)
```





8) Clustering of Users and prediction of genders via clustering?

I want to also try hierarchical clustering with this data. I will do both agglomerative and divisive. Firstly, agglomerative:

```{r}
users[] <- lapply(users, as.factor)
users2 <- users %>% dplyr::select(-user_id, -location, -user_age)
# Compute dissimilarity matrix
gower_dist <- daisy(users2, metric = "gower")

```

```{r}

# Hierarchical clustering
hc <- hclust(gower_dist, method = "average")  # other methods: "complete", "single", "ward.D2"

```
I plan to use the silhouette statistic to get the number of clusters
```{r}
sil_width <- c()
for(k in 2:20){
  clusters <- cutree(hc, k)  # hierarchical on sample
  sil <- silhouette(clusters, gower_dist)
  sil_width[k] <- mean(sil[, 3])
}

df_sil <- data.frame(
  k = 2:20,
  sil = sil_width[2:20]
)

# UNC Carolina blue
unc_blue <- "#4B9CD3"

ggplot(df_sil, aes(x = k, y = sil)) +
  geom_line(color = "#4B9CD3", size = 1.3) +
  geom_point(size = 3, color = "#4B9CD3", fill = "#13294B", shape = 21) +
  theme_bw(base_size = 14) +
  labs(
    x = "Number of Clusters",
    y = "Average Silhouette Width",
    title = "Silhouette Width vs Number of Clusters"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(face = "bold"),
    panel.border = element_blank(),
    axis.line = element_line(color = "black")
  )
ggsave('figures/silhouette_width.png')
```

From this plot, it seems as though 13 clusters is best (highest point before decrease). Thus, I will trim the tree at 13 clusters. I because the dendrogram will be to dense to serve as a useful visualization, I will instead use a t-SNE plot.

```{r}
clusters_13 <- cutree(hc, k = 13)

tsne_res <- Rtsne(
  as.matrix(gower_dist),
  is_distance = TRUE,
  perplexity = 30
)

tsne_df <- data.frame(
  X1 = tsne_res$Y[,1],
  X2 = tsne_res$Y[,2],
  cluster = factor(clusters_13)
)
base_theme <- theme_bw(base_size = 14) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(face = "bold"),
    panel.border = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "right"
  )

ggplot(tsne_df, aes(x = X1, y = X2, color = cluster)) +
  geom_point(size = 1, alpha = 0.8) +
  labs(
    title = "t-SNE Visualization of 13 Clusters",
    x = "t-SNE Dimension 1",
    y = "t-SNE Dimension 2",
    color = "Cluster"
  ) +
  base_theme

ggsave('figures/tsne_aggclus.png')
```

Was going to try divisive hierarchical clustering, but I feel like this gives the general gist of things. That and the function 'diana()' typically used for divisive hierarchical clustering doesn't work well because my data is too big/ there are too many observations.


